On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-01-24 TTau_Halpha/kurosawa.tex
Minor change. (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@628 25464f21-6099-402c-b30a-640f1d40d38b
a minor update.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@629 25464f21-6099-402c-b30a-640f1d40d38b

Clearly there are several alternative outflow scenarios. Here we adopt
two simple kinematical models which broadly represent the results of
MHD simulations. The first is a bipolar wind model, in which the
outflow is collimated along the rotational axes (a model similar to
that of \citealt{krasnopolsky:2003} in large scale, $>10$~au). The
second model is based on the disc-wind paradigm, in which the density
of the outflow increases towards the equatorial plane. The difference
in latitudinal density structure between the two outflow models should
provide an indication as to whether line profiles alone can be used to
constrain the outflow geometry. In the following sections we present
details of the two outflow structures.

>>>>

Clearly there are several alternative outflow scenarios. Here we adopt
two simple kinematical models which broadly represent the results of
MHD simulations. The first is a bipolar wind model, in which the
outflow is collimated along the rotational axes (a model similar to
that of \citet{krasnopolsky:2003} in large scale, $>10$~au). The
second model is based on the disc-wind paradigm, in which the density
of the outflow increases towards the equatorial plane. The difference
in latitudinal density structure between the two outflow models should
provide an indication as to whether line profiles alone can be used to
constrain the outflow geometry. In the following sections we present
details of the two outflow structures.
